Cover letter

### 2025-01-08 cover-letter.qmd
Update cover letter for BMJ Open

I am submitting our manuscript, “Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study” for consideration for publication in JAMA Surgery.

@@

This manuscript has not been published or submitted to any journal, but it has been posted on the pre-print server medRxiv: https://doi.org/10.1101/2024.03.13.24304236. No other related papers from this study have been published, posted, or submitted.

>>>>

I am submitting our manuscript, “Feasibility of a Cluster Randomised Trial on the Effect of Trauma Life Support Training: A Pilot Study” for consideration for publication in BMJ Open, the protocol of which was published in your journal in 2020 (https://bmjopen.bmj.com/content/12/4/e057504).

@@

This manuscript has not been published or submitted to any journal, but it has been posted on the pre-print server medRxiv (https://doi.org/10.1101/2024.03.13.24304236). No other related papers from this study have been published, posted, or submitted.
